\documentclass[11pt]{article}

\begin{document}

\begin{center}
\emph{\textbf{\textit{FLUTTER (GOOGLE DEVELOPMENT PRODUCT)}}}
\end{center}
Flutter
Flutter is Google’s mobile UI framework for crafting high-quality native interfaces on iOS and Android in record time. Flutter works with existing code, is used by developers and organizations around the world, and is free and open source.

The Flutter mobile app SDK is a new way to build fast, beautiful mobile apps that helps developers break away from “cookie cutter” apps that have been so common in the past.
As with any new system, people want to know what makes Flutter different, or put another way, “what is new and exciting about Flutter?” That is a fair question, and this article will try to answer it from a technical viewpoint — not just what is exciting, but why.(Wm Leler,\cite{Leler}).

Flutter gives developers an easy and productive way to build and deploy beautiful and performant mobile apps on both Android and iOS. What makes it unique is that it neither uses web views nor iOS/Android UI components but still draws everything natively using its own rendering engine.

Instead of reinventing the wheel, the Flutter team looked extensively at the projects inside Google and reused as much of the existing code as it made sense. They took relevant pieces from Chrome, WebKit, Android and built a slim C++ engine. They chose to build the rest of the framework using Dart. The framework implements animation, painting, gestures, rendering, and provides an implementation of Material Design components as well as a sparse iOS-themed component library.(Korhan Bircan,\cite{Korhan}).

Flutter is Google’s open source toolkit for helping developers build iOS and Android apps. It’s not necessarily a household name yet, but it’s also less than a year old and, to some degree, it’s going up against frameworks like Facebook’s popular React Native. Google’s framework, which is heavily focused around the company’s Dart programming language, was first announced at Google’s I/O developer conference last year.(Frederic Lardinois,\cite{Frederic}).

Flutter is a new mobile development SDK brought to you by Google to help you build fast, beautiful, and cross-platform mobile applications. It uses a new language called Dart. If you are worried about having to learn a whole new programming language to build Flutter Apps, don’t be! Dart is majorly influenced by languages like JavaScript and Java. This helps reducing the learning curve significantly.

The key advantage of Flutter is that it provides reactive views without the need for JavaScript Bridge, hence improving the performance significantly. Another advantage is use of widgets. In Flutter, Everything’s a Widget.(Ankur Kedia,\cite{Ankur}).



\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}